---
title: "Recreation, Ogran et al. 2019, figure 3"
author: "Jill Syrotchen"
date: "10/17/2020"
output:
  pdf_document: default
bibliography: bibliography.bib
---

Step 1: finding the data

  -Data were fairly easily accessible through a link in the paper (https://doi.10.5061/dryad.b2rbnzs93). Clicking the link directly would not load the page for me, so I went to https://doi.org and typed in 10.5061/dryad.b2rbnzs93 to the search bar, which loaded this DRYAD page: https://datadryad.org/stash/dataset/doi:10.5061/dryad.b2rbnzs93. From that page I was able to download the complete .xlsx dataset for the paper.
  
  -I then converted the .xlsx dataset to a .csv file.
  
  -I was not able to find any code.
  
  
  
Step 2: loading data into R

  -Data loaded into R fine, but due to formatting every other row was blank and showed as NA. To eliminate the empty rows I used a function from dplyr (see #remove blank rows).
  
  
  
Step 3: manipulating the data
  
  -Stuck on getting the dataset sorted to individual trait:treatment sets so I can plot them. I tried to group by population and treatment and then summarize for mean glucosinolates first, which didn't work, but I thought it might be because of its units symbol. 
  
  -Tried str() on the full dataset to see if any spaces were throwing off the table (hopefully this is the right function that would remove stray spaces?)
  
  -So then I tried summary next for dry weight (DW) and got the same result - the group_by works but the rest of the table says NA.
  
  -SOLUTION: had to use fancy `` symbols for the names of columns to get the commands to work!
  

```{r setup, include=TRUE, message=FALSE}

library("tidyverse")
library("dplyr")
library("ggplot2")
library("magrittr")
library("knitr")

full_dataset<-read_csv("./data/Full_dataset_Ogran_et_al.csv")

#remove blank rows
full_dataset <- full_dataset %>% filter_all(any_vars(!is.na(.)))

#grouping subset of treatments and groups plotted, and standard error
subset_trt <- full_dataset %>% group_by(Population, Treatment) %>% dplyr::summarize(
  Glucosinolates = mean(`Total glucosinolates (µmol/g DW)`, na.rm = TRUE), 
  Trypsin_PI = mean(`Trypsin-PI (%)`, na.rm = TRUE), 
  Trichome_density = mean(`Trichomes`, na.rm = TRUE), 
  Bolting_time = mean(`Bolting time (days)`, na.rm = TRUE), 
  Dry_weight = mean(`DW (g)`, na.rm = TRUE),
  gluc_se = sd(`Total glucosinolates (µmol/g DW)`, na.rm = TRUE)/sqrt(length(na.omit(
    `Total glucosinolates (µmol/g DW)`))),
  trypsin_se = sd(`Trypsin-PI (%)`, na.rm = TRUE)/sqrt(length(na.omit(`Trypsin-PI (%)`))),
  trichome_se = sd(`Trichomes`, na.rm = TRUE)/sqrt(length(na.omit(`Trichomes`))),
  bolting_se = sd(`Bolting time (days)`, na.rm = TRUE)/sqrt(length(na.omit(
    `Bolting time (days)`))),
  dw_se = sd(`DW (g)`, na.rm = TRUE)/sqrt(length(na.omit(`DW (g)`)))
  )

knitr::kable(subset_trt,digits=2,caption="Grouped trait treatments and their standard errors")
```

Step 4: creating the reaction norm figures

  -Using ggplot 2, I assembled a very basic graph starting with glucosinolates first. 
  
  -Used geom_point at first and tried geom_line to get lines to connect between points, but it connected points within treatments instead.
  
  -SOLUTION: used aes(group) to group by population, which made lines between population points!
  
  -Now doing stylistic edits to get the graph to really look like the figures from the paper. 
  
  -STUCK: formatting the y axis to show the scaling it does in the paper.
  -SOLVED: scale_y_continuous(limits=c(10,22), breaks = seq(10,22,by = 2))
  
  -STUCK: Need to figure out what I need to do to make error bars on each point.
  -SOLVED: calculated SEM for each trait and added it to the dataset
  
  
```{r plotting, include=TRUE}

#Glucosinolates
gluc <- ggplot(data=subset_trt)+   
  aes(x=Treatment)+
  aes(y=Glucosinolates)+
  aes(group=Population)+
  aes(color=Population)+
  aes(fill=Population)+
  aes(shape=Population)+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(y=Glucosinolates, ymin=Glucosinolates-gluc_se,
                    ymax=Glucosinolates+gluc_se), width = 0.05)+
  scale_shape_manual(values=c(17,15))+
  scale_color_manual(values=c("blue","red"))+
  scale_fill_manual(values=c("blue","red"))+
  ylab("Glucosinolates")+
  scale_y_continuous(limits=c(10,22), breaks = seq(10,22,by = 2))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
plot(gluc)

#Trypsin PI
TPI <- ggplot(data=subset_trt)+   
  aes(x=Treatment)+
  aes(y=Trypsin_PI)+
  aes(group=Population)+
  aes(color=Population)+
  aes(fill=Population)+
  aes(shape=Population)+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(y=Trypsin_PI, ymin=Trypsin_PI-trypsin_se, 
                    ymax=Trypsin_PI+trypsin_se), width = 0.05)+
  scale_shape_manual(values=c(17,15))+
  scale_color_manual(values=c("blue","red"))+
  scale_fill_manual(values=c("blue","red"))+
  ylab("Trypsin PI activity (%)")+
  scale_y_continuous(limits=c(30,65), breaks = seq(30,65,by = 5))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
plot(TPI)

#Trichome density
trichome <- ggplot(data=subset_trt)+   
  aes(x=Treatment)+
  aes(y=Trichome_density)+
  aes(group=Population)+
  aes(color=Population)+
  aes(fill=Population)+
  aes(shape=Population)+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(y=Trichome_density, ymin=Trichome_density-trichome_se, 
                    ymax=Trichome_density+trichome_se), width = 0.05)+
  scale_shape_manual(values=c(17,15))+
  scale_color_manual(values=c("blue","red"))+
  scale_fill_manual(values=c("blue","red"))+
  ylab("Trichome density")+
  scale_y_continuous(limits=c(1,5), breaks = seq(1,5,by = 1))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
plot(trichome)

#Bolting

#Dry weight


```

#Bibliography
[@Ogran2019-td]